Inefficient Concessions and Mediation

### 2020-12-05 notes.tex
Add calculations for minimum gift in e<1 case

				\item Now solve for $e$ starting from Expression~\ref{eq:split}:
					$$pg - \left(1 - \de \right) \left( T + D \right) \geq pge + eg \left( T - \de T + W \right)$$
					\begin{equation}
						pg - \left(1 - \de \right) \left( T + D \right) \geq eg \left( p + T - \de T + W \right)
						\label{eq:g5}
					\end{equation}
						\begin{itemize}
							\item {\color{red} $g \left( p + T - \de T + W \right)$ is non-negative as long as $g$ is positive}: $p, 1-\de, T$ and $W$ are all assumed non-negative and $T+D > W$ so that $T$ is strictly positive. It can only possibly be zero if $p=0$ and $\de = 1$.
								\begin{itemize}
									\item For the IC constraint to hold then (with non-negative gifts), we must at least have {\color{red} $pg - \left(1 - \de \right) \left( T + D \right)$ non-negative, which requires $g$ to be set according to Expression~\ref{eq:g3}}. This only works if $e$ is set to zero; otherwise we need to look back at Expression~\ref{eq:g2}. This is just a weak condition that, if violated, means the IC constraint does not hold.
								\end{itemize}
							\item If {\color{red} $g \left( p + T - \de T + W \right)$ is positive}, we can divide through to get
								$$\frac{pg - \left(1 - \de \right) \left( T + D \right)}{g \left( p + T - \de T + W \right)} \geq e$$
						\end{itemize}
					\item To get a sense of the magnitudes, I will plug $g = p \left(T+D\right)$ from the $e=0$ CSE case (just because it's easier to work with than the optimal gift when $e=1$ into Expression~\ref{eq:g5}. First I divide through by $g$ {\color{blue}(this is okay if $g$ is assumed to be positive)}
						\begin{equation}
							p - \frac{\left(1 - \de \right) \left( T + D \right)}{g} \geq e \left( p + T - \de T + W \right)
							\label{eq:g6}
						\end{equation}
						$$p - \frac{\left(1 - \de \right) \left( T + D \right)}{p \left(T+D\right)} \geq e \left( p + T - \de T + W \right)$$
						$$p - \frac{1 - \de}{p } \geq e \left( p + T - \de T + W \right)$$
							\begin{itemize}
								\item For the LHS to be positive, we need $p^2 \geq 1 - \de$, e.g. if $p = 0.5$, we need $\de \geq .75$
								\item Parameterization that is in the paper now:
									\begin{itemize}
										\item Let $T = 10$, $W=8$ and $D = 5$
										\item Threshold for high types to separate when concessions do not have future material value is $\de = \frac{8}{10+5} = .5\overline{3}$. Let $\de_h = .6$ and $\de_l = .3$. Assume $p = .2$. By Theorem 2, separation through concessions is possible.
										\item Minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$
										\item Minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
									\end{itemize}
							\end{itemize}

			\end{itemize}
		\item \color{ForestGreen} No notes to digitize right now
			\begin{itemize}
				\item Calculate maximum $e$ from Expression~\ref{eq:g6} using parameterization from paper
					\begin{itemize}
						\item Do it under simple $g$ and the more complicated $g$ from Expression~\ref{eq:g4}
						\item Compare to calculations in example from text
						\item Try another parameterization with $p$ larger so it works
					\end{itemize}
				\item Check parameter restrictions for existence of equilibria in Section 4.2
			\end{itemize}
	\end{itemize}

>>>>

				\item Now solve for $e$ starting from Expression~\ref{eq:split}:
					$$pg - \left(1 - \de \right) \left( T + D \right) \geq pge + eg \left( T - \de T + W \right)$$
					\begin{equation}
						pg - \left(1 - \de \right) \left( T + D \right) \geq eg \left( p + T - \de T + W \right)
						\label{eq:g5}
					\end{equation}
						\begin{itemize}
							\item {\color{red} $g \left( p + T - \de T + W \right)$ is non-negative as long as $g$ is positive}: $p, 1-\de, T$ and $W$ are all assumed non-negative and $T+D > W$ so that $T$ is strictly positive. It can only possibly be zero if $p=0$ and $\de = 1$.
								\begin{itemize}
									\item For the IC constraint to hold then (with non-negative gifts), we must at least have {\color{red} $pg - \left(1 - \de \right) \left( T + D \right)$ non-negative, which requires $g$ to be set according to Expression~\ref{eq:g3}}. This only works if $e$ is set to zero; otherwise we need to look back at Expression~\ref{eq:g2}. This is just a weak condition that, if violated, means the IC constraint does not hold.
								\end{itemize}
							\item If {\color{red} $g \left( p + T - \de T + W \right)$ is positive}, we can divide through to get
								$$\frac{pg - \left(1 - \de \right) \left( T + D \right)}{g \left( p + T - \de T + W \right)} \geq e$$
						\end{itemize}
					\item To get a sense of the magnitudes, I will plug $g = p \left(T+D\right)$ from the $e=0$ CSE case (just because it's easier to work with than the optimal gift when $e=1$ into Expression~\ref{eq:g5}. First I divide through by $g$ {\color{blue}(this is okay if $g$ is assumed to be positive)}
						\begin{equation}
							p - \frac{\left(1 - \de \right) \left( T + D \right)}{g} \geq e \left( p + T - \de T + W \right)
							\label{eq:g6}
						\end{equation}
						$$p - \frac{\left(1 - \de \right) \left( T + D \right)}{p \left(T+D\right)} \geq e \left( p + T - \de T + W \right)$$
						$$p - \frac{1 - \de}{p } \geq e \left( p + T - \de T + W \right)$$
							\begin{itemize}
								\item For the LHS to be positive, we need $p^2 \geq 1 - \de$, e.g. if $p = 0.5$, we need $\de \geq .75$
								\item Parameterization that is in the paper now:
									\begin{itemize}
										\item Let $T = 10$, $W=8$ and $D = 5$
										\item Let $\de_h = .6$ and $\de_l = .3$. Assume $p = .2$. 
										\item Threshold for high types to separate when concessions do not have future material value is $\de = \frac{8}{10+5} = .5\overline{3}$. By Theorem 2, separation through concessions is possible.
										\item Minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$
										\item Minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
										\item Minimum $e$ from Expression~\ref{eq:g6}:
											\[
											  0.2 - \frac{\left(1 - 0.3 \right) \left( 10 + 5 \right)}{g} \geq e \left( 0.2 + 10 - 0.3\cdot 10 + 8 \right)
											\]
											\[
											  0.2 - \frac{0.7 \left( 15 \right)}{g} \geq e \left( 11.2 \right)
											\]
											\[
											  \frac{0.2}{11.2} - \frac{0.7 \left( 15 \right)}{11.2g} \geq e 
											\]
											\[
											  0.01786 - \frac{9.375}{g} \geq e 
											\]
										To keep $e \geq 0$, we need $g \geq 525$ (this is REALLY big compared to $W$ for instance). It's also huge compared to the optimal gifts when $e=0$ of 3 and when $e=1$ of $0.\overline{63}$.
									\end{itemize}
								\item Now let's try the same parameterization with $p=0.9$.
									\begin{itemize}
										\item Minimum $e$ from Expression~\ref{eq:g6}:
											\[
											  0.9 - \frac{\left(1 - 0.3 \right) \left( 10 + 5 \right)}{g} \geq e \left( 0.9 + 10 - 0.3\cdot 10 + 8 \right)
											\]
											\[
											  0.9 - \frac{0.7 \left( 15 \right)}{g} \geq e \left( 11.9 \right)
											\]
											\[
											  \frac{0.9}{11.9} - \frac{0.7 \left( 15 \right)}{11.9g} \geq e 
											\]
											\[
											  0.07563 - \frac{8.8235}{g} \geq e 
											\]
										To keep $e \geq 0$, we need $g \geq 116.66$. This is still nearly an order of magnitude larger than $W$, and both the optimal gifts when $e=0$ of 13.5 and when $e=1$ of $\frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = \frac{0.9(0.7)(15)}{0.7 \cdot (1-0.9)+(.1)5} = \frac{0.63\cdot15}{0.7 \cdot 0.1+.5} = 16.58$.
									\end{itemize}
							\end{itemize}

			\end{itemize}
		\item \color{ForestGreen} No notes to digitize right now
			\begin{itemize}
				\item Check parameter restrictions for existence of equilibria in Section 4.2
				\item Obviously we can come up with other parameterizations in which this may look a little more reasonable
					\begin{itemize}
						\item But I think the first step is to calculate the high-type utility under the different scenarios and the different gifts and see what happens (since you get the indirect benefit of the gift--or do you since $e$ is too small?)
					\end{itemize}
			\end{itemize}
	\end{itemize}
